\begin{abstract}
Many graph-based workloads require performing \emph{subgraph matching} by finding all subgraphs of a data graph that are isomorphic to a
input query graph. Doing so on a real-life data graph is often computation-intensive because of the large number of graph vertices to be
examined. Existing schemes for subgraph matching all adopt a simple scheme by matching vertices of a query graph one by one. This
strategy fails to capitalize on the structure parallelism of graphs and can incur extensive memory accesses on GPUs. This work presents
\SystemName, a new GPU-based subgraph matching scheme that can match multiple query vertices simultaneously. Unlike prior work,
\SystemName performs subgraph matching within a single GPU kernel, eliminating many memory access operations required to process the
intermediate results. \SystemName also provides an enhanced storage format to reduce the memory footprint of graph data and improve
processing efficiency. We evaluate our approach by applying it to eight real-life graph datasets on an NVIDIA 2080Ti GPU. Experimental
results show that our approach improves GSI, the state-of-the-art graph matching framework, by 16\% on average (up to \FIXME{xx}\%),
while reducing the memory footprint by 83\%.


%Subgraph search finds all subgraphs of a data graph that are isomorphic to a query graph. It is a fundamental operation in many application
%fields like analysis of protein-protein interaction network and community detection. Existing works adopt a simple search procedure that
%matches vertices of a query graph one by one, which incurs a large number of memory accesses during reading and writing intermediate
%results. In this work, we perform subGraph sEarch usiNg parallEl Vertex mAtching (\SystemName). Specifically, \SystemName can match as many
%query vertices as possible at each iteration and generate corresponding results in one GPU kernel. Compared to GSI, which is the
%state-of-the-art GPU-based subgraph search method, our approach achieves an average speedup of $5\times$. Additionally, we optimize the
%data graph format of GSI by replacing its hash indexes with interval indexes. The proposed interval-index format reduces the space cost and
%searching time of hash-index format by 83\% and 58\% respectively. To validate the effectiveness of parallel vertex matching, we also
%compare it to the single vertex matching devised based on our  parallel vertex matching. Results show that our approach improves the single
%vertex matching by 15.9\% on average.

%Based on properties of the data graph, there are many types of subgraph matching. In this work, we focus on matching query graphs on a labeled undirected data graph with the acceleration of GPU.
\end{abstract}
